---
title: "MAP_training"
author: "JK"
date: "2024-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Welcome to MAP-East Africa node ECR training program for Cohort 1 (2024-2025). This program builds on the "[Introduction of Spatial Analysis for Infectious diseases tutorial](https://malaria-atlas-project.gitlab.io/intro-to-spatial-analysis-for-infectious-diseases/index.html)" material.

# Let's start with installing R packages 
```{r}
list.of.packages <- c("tidyverse", "sf", "terra", 
#"rgdal", 
"sp", "raster", "scico", "RColorBrewer", "viridis", "viridisLite", "ggplot2", "tidyr", "dplyr", "readxl")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

Please note that "#" before a line of code means "Ignore"/"Do not run" to R. 
"rgdal" package was retired in 2023 so it has been "switched off" for the newer R versions but if you get any error messages regarding other R packages needing "rgdal", an earlier version of R needs to be installed and used. 

```{r}
library(tidyverse)
library(sf)
library(terra)
#library(rgdal)
```







